---
name: Marvin
surname: Castrejon
position: "Marketing Analytics & Insights Professional"
phone: +1 (831) 444-2170
www:
email: "mcastrejon@cpp.edu"
github: macast7
linkedin: linkedin.com/in/marvin-castrejon
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::latexcv:
    theme: classic
header-includes:
   - \usepackage{enumitem}
   - \setlist[itemize]{nosep, left=0pt}
   - \setlist[enumerate]{nosep, left=0pt}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

if (!requireNamespace(c("tinytex","vitae","tibble"), quietly = TRUE)) {
  install.packages(c("tinytex","vitae","tibble"))
}

if (Sys.which("pdflatex") == "" && !tinytex::is_tinytex()) {                    
  message("► TinyTeX not found – installing")
  tinytex::install_tinytex()        
} else {
  message("✓ LaTeX present – no installation needed.")
}

library(vitae)
library(tibble)
```

# Professional Summary

Motivated and detail-oriented marketing and analytics professional with a strong background in data interpretation, forecasting, and survey research. Skilled in transforming complex data into clear insights that inform business and academic decisions. Experienced with tools such as R, Quarto, and ggplot2 in both professional and academic settings.

# Technical Skills

-   **Programming Languages:** R, Python, SQL\
-   **Web & Visualization Tools:** HTML, CSS, Quarto, ggplot2, Google Analytics
-   **Analytics Areas:** Time Series Forecasting, Survey Analysis, Topic Modeling, MANOVA, Data Wrangling

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ College, ~ Institution,
  "M.S. Digital Marketing", "2023 – 2025", "College of Business", "Cal Poly Pomona",
  "B.A. International Business and Marketing", "2021 – 2023", "College of Business", "Cal Poly Pomona"
) %>%
  detailed_entries(Degree, Year, College, Institution)
```

# Work Experience

```{r}
tribble(
  ~ Years, ~ Company, ~ Duties, ~ Title,
  
  "June 2024 – July 2024", "Cal Poly Pomona Farm Store",
  list(
    "Analyzed 12 months of sales data across multiple product categories to identify top-performing items.",
    "Created visualizations (bar plots, boxplots, scatterplots) using R and ggplot2 to support business insights.",
    "Delivered recommendations to improve category-level strategy based on gross sales, profit margins, and customer preferences.",
    "Tools: R, readxl, tidyverse, ggplot2, Excel."
  ),
  "Data & Marketing Intern",
  
  "Jan 2025 – Present", "Freelance / Upwork",
  list(
    "Completed various client projects involving survey analysis, Google Sheets dashboards, and campaign reporting.",
    "Built interactive reports and provided actionable insights for e-commerce and service-based businesses.",
    "Communicated with non-technical clients to clarify project goals and present results clearly.",
    "Tools: R, Python, Google Sheets, Excel, Canva, Google Analytics."
  ),
  "Freelance Marketing & Analytics Consultant"
  
) %>%
  detailed_entries(
    what = Title,
    when = Years,
    with = Company,
    why = Duties
  )
```